---
title: "Activity Report"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 300)

```


<Div custom-style = "Publication subtitle">  </Div>
Extract date: `r format(Sys.Date(), '%d %B %Y')`    
Contact: [Bennyy](mailto:harleyb101010@gmail.com)   

## Background

This is the IMRP's activity report which is based on faction rosters across the entire community. This report is generic and can be used for every faction.

## List of Tier 0's
```{r table_0, ft.align="left"}
Faction_Roster_List_Tier0_Table

```

## List of Tier 1's
```{r table_1, ft.align="left"}
Faction_Roster_List_Tier1_Table

```

## Condition Table
```{r table_7, ft.align="left",fig.width=7, fig.height=4}
Activity_Type_Condition_Table_Output

```


## Tier 0 Activity Type Graph

This is the number of members by activity type who are tier 0. The list of conditions are published in a table above.
```{r table_3, ft.align="left",fig.width=7, fig.height=4}
bar_graph_tier0_activity

```

## Tier 1 Activity Type Graph

This is the number of members by activity type who are tier 1. The list of conditions are published in a table above.
```{r table_4, ft.align="left", fig.width=7, fig.height=4}
bar_graph_tier1_activity

```



## Tier 2 Activity Type Graph

This is the number of members by activity type who are tier 2. The list of conditions are published in a table above.
```{r table_5, ft.align="left",fig.width=7, fig.height=4}
bar_graph_tier2_activity

```


## Tier 3 Activity Type Graph

This is the number of members by activity type who are tier 3. The list of conditions are published in a table above.
```{r table_6, ft.align="left",fig.width=7, fig.height=4}
bar_graph_tier3_activity

```