---
title: "Activity Report"
author: "Bennyy"
date: "2024-10-19"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 300)

```


<Div custom-style = "Publication subtitle">  </Div>
Extract date: `r format(Sys.Date(), '%d %B %Y')`    
Contact: [Bennyy](mailto:harleyb101010@gmail.com)   

## Background

This is the IMRP's activity report which is based on faction rosters across the entire community. This report is generic and can be used for every faction. If you have any questions please contact Bennyy

## List of Tier 0's
```{r table_0, ft.align="left"}
Faction_Roster_List_Tier0_Table

```

## List of Tier 1's
```{r table_1, ft.align="left"}
Faction_Roster_List_Tier1_Table

```

## Member Count by Tier

This is the number of members by tier in the faction. 
```{r table_2, ft.align="left"}
Faction_Roster_Count_Table

```

## Tier 0 Activity Type Graph

This is the number of members by tier in the faction. 
```{r table_3, ft.align="left"}
bar_graph_tier0_activity

```

## Tier 1 Activity Type Graph

This is the number of members by tier in the faction. 
```{r table_4, ft.align="left"}
bar_graph_tier1_activity

```



## Tier 2 Activity Type Graph

This is the number of members by tier in the faction. 
```{r table_5, ft.align="left"}
bar_graph_tier2_activity

```


## Tier 3 Activity Type Graph

This is the number of members by tier in the faction. 
```{r table_6, ft.align="left"}
bar_graph_tier3_activity

```